Mixed Precision Euclidean Distance Calculations using GPU Tensor Cores and Applications to Similarity Searches

### 2025-04-13 Paper/figures/Register_Based_Fragment.tex
Scaled diagrams for paper.
Added paper from overleaf because compiles timed out.

	\newcommand\drawThreadPhase[1]{
		\edef\phaseNum{#1}
% Thread\register layout
		\foreach \phaseRow in {0, ..., 7} {
			\foreach \phaseCol in {0, ..., 3}{
				\coordinate (C) at (\phaseCol * \registerWidth, -\phaseRow * \registerHeight);
				\pgfmathsetmacro\threadIndex{int(\phaseRow * 4 + \phaseCol)}
				\def\chunkColor{\getPhaseColor{\phaseNum}}
				\filldraw[fill=\chunkColor, draw=black] (C) rectangle +(\registerWidth, -\registerHeight) node[midway, font=\small] {\texttt{T\threadIndex}};
			}
		}
	}

>>>>

	\newcommand\drawThreadPhase[1]{
		\edef\phaseNum{#1}
% Thread\register layout
		\foreach \phaseRow in {0, ..., 7} {
			\foreach \phaseCol in {0, ..., 3}{
				\coordinate (C) at (\phaseCol * \registerWidth, -\phaseRow * \registerHeight);
				\pgfmathsetmacro\threadIndex{int(\phaseRow * 4 + \phaseCol)}
				\def\chunkColor{\getPhaseColor{\phaseNum}}
				\filldraw[fill=\chunkColor, draw=black] (C) rectangle +(\registerWidth, -\registerHeight) node[midway, font=\tiny] {\texttt{T\threadIndex}};
                % Draw node labels for how A[n] matches up to this layout.
                \ifnum \threadIndex=0
                \coordinate (LabelPos) at ($(C)+(-0.15, 0.2)$);
                \coordinate (ArrowEnd) at ($(C)+(\halfRegisterWidth, 0)$);

                \pgfmathtruncatemacro\indexNum{\phaseNum - 1}
                \node[font=\tiny] (label) at (LabelPos) {\texttt{A[\indexNum]}};
                \draw[arrows= -{Stealth[length=1mm]}] (label.east) .. controls +(0.12, 0) .. (ArrowEnd);
                \fi

			}
		}
	}
